### 2019-09-18 main.tex

\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{eso-pic}
\usepackage{soul}
\usepackage{xcolor}
% \usepackage{background}
\usepackage{float}
\usepackage[top=2cm, bottom=2cm, outer=2cm, inner=2cm]{geometry}
\setcounter{tocdepth}{3}
% \setcounter{secnumdepth}{3}

@@

% \backgroundsetup{
% scale=1,
% angle=-90,
% opacity=.4,  %% adjust
% contents={\includegraphics[width=\paperwidth,height=\paperheight]{earth1.png}}
% }

@@

>>>>

\documentclass[11pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{eso-pic}
\usepackage{soul}
\usepackage{xcolor}

\usepackage{gfsdidot} % Use the GFS Didot font: http://www.tug.dk/FontCatalogue/gfsdidot/
\usepackage{microtype} % Improves typography

\usepackage{fancyhdr}
% \usepackage{pagecounting}
% \usepackage[dvips]{color}

\newcommand{\illinoislogo}{\includegraphics[height=0.5in]{images/illinoislogo.png}}
\newcommand{\anslogo}{\hspace{-4mm}\includegraphics[height=0.5in]{images/ansuiuc.png}}
\newcommand{\anssite}{ans.npre.illinois.edu}
% \usepackage{background}
\usepackage{float}
\usepackage[top=2cm, bottom=2cm, outer=2cm, inner=2cm]{geometry}
\setcounter{tocdepth}{3}
% \setcounter{secnumdepth}{3}
\usepackage{environ}
\NewEnviron{letter}{%
  \input{structure}
  \opening
  \closing
}

@@

% Creates the flow chart for conference management
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}

\tikzstyle{chair} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=blue!30]
\tikzstyle{director} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=orange!30]
\tikzstyle{coordinator} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=white!30]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

\pagestyle{fancy}
\lhead{\anslogo}
\rhead{\illinoislogo}

### 2019-09-18 theme.tex
fixes makefile and fixes theme.tex uiuc.tex

\section{Theme}

\Huge{Saving the World One Atom at a Time}\\

There are many challenges facing the world today. Some of these have been designated existential threats to humanity. As students, these obstacles may appear insurmountable. The ANS Student Conference is a marvelous opportunity to inspire optimism for the future as researchers, professionals, and students, gather to showcase critical advances in technology. Nuclear, plasma, and radiological engineering will be central to endeavors like solving the world's energy needs, developing technology that will take us to the stars, treating cancer, and many others.  Our goal is to inspire and motivate students in these fields to tackle grand challenge problems. Students will hear from visionary speakers and leaders of the nuclear science community. They will leave with renewed hope for the future and the knowledge that their efforts are saving the world, one atom at a time.\\
The University of Illinois at Urbana-Champaign would honored to host the ANS Student Conference in 2021 and to share the innovative and galvanizing environment of our great campus.

>>>>

\section{Saving the World One Atom at a Time}
There are many challenges facing the world today and some have been designated existential threats to humanity. Young people today will witness the growing toll of anthropogenic climate change. As students, obstacles at the scale of the world climate crisis appear daunting and overwhelming. We believe that many solutions will come from the nuclear sciences. The ANS student conference is an opportunity for students and professionals to come together and share advances in critical technology and research, dedicated to solving these problems. Whether the problem is solving the world’s energy needs, developing technology that will take us to the stars, or curing cancer, nuclear, plasma, and radiological engineering will be at the center of those endeavors. Our goal is to inspire and motivate students in nuclear, plasma, and radiological engineering fields to tackle big problems. Saving the world one atom at a time reflects the fact that nuclear science is a powerful force in dealing with grand challenge problems. This theme also honors the individual, atomic, contributions from students, researchers, and professionals, in the field of nuclear engineering, that are essential to progress. This conference is about science and it is about the people that make the science possible. Students will hear from visionary speakers and leaders of the nuclear science community and come away with optimism for the future; knowing that they are saving the world one atom at a time.\\
The University of Illinois at Urbana-Champaign chapter of ANS would be honored to host the 2021 student conference. We hope to create an atmosphere that will galvanize students and professionals for the exciting future of nuclear engineering.
